\chapter{Mateti's {\LaTeX} Thesis Example}

Download link: \url{http://www.cs.wright.edu/~pmateti/GradStudents/thesisExample.tbz}
I recommend that you use my collection of thesis files that you can
download from here.  My own contribution here is not original.  It is
in pulling together various needed pices in trying to reduce the
LaTeX-learning time for my students.

\section{Contents of the {\tt tar} File}

The downloaded file is a tar archive compressed with bzip2.  You can
untar it as in

{\tt tar xvfj thesis.tbz}

Your current directory will then have a new subdirectory called
Thesis/ with the following files and subdirectories in it.

\begin{verbatim}
% ls -l Thesis
total 36
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 13:07 Chapters/
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 11:44 Figures/
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 11:44 LaTeX/
-rw-r--r--    1 pmateti  pmateti       713 May 24 11:47 Makefile
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 13:09 Tables/
-rw-r--r--    1 pmateti  pmateti      8513 May 24 11:44 thesis.bib
-rw-r--r--    1 pmateti  pmateti      1158 May 24 11:47 thesis.tex
drwxr-xr-x    2 pmateti  pmateti      4096 May 24 11:44 WSU/

\end{verbatim}

\section{Your Use of these Files}

The files in the directory LaTeX are to be left as they are; edit
these only if you are fluent in LaTeX.  Edit the files in the WSU
directory to insert your own name etc.  Replace all the files in the
{\tt Chapters/ Figures/ Tables/} directories with yours.  Edit the
thesis.tex to input the files in the {\tt Chapters/ Figures/ Tables/}
directories.

Use the given Makefile as a template and adjust.

% -eof-
